R Notebook

### 2022-07-22 Code/Simulation.Rmd
ARMA(1,1) dependence model with updated figures

```{r packages}
# Load packages
library(tidyverse)
library(copula)
library(evd)
library(ismev)
library(tseries)
source('tspb.R')
```

@@

```{r AR(1) D}
test_copula_D <- function(x, dist, B, mean, sd) {

@@

    stat  <- ks.test(x, dist, mean = mean, sd = sd)$statistic

@@

        # Transform bootstrap sample and fit the parameters
        x.b <- qnorm(u, mean = mean, sd = sd)

        # Gather bootstrap sample's test statistic
        stat.b[i] <- ks.test(x.b, dist, mean = mean, sd = sd)$statistic
    }

@@

# Standard KS test
test_standard_ks <- function(x, mean, sd) {
  p.value <- ks.test(x, "pnorm", mean = mean, sd = sd)$p.value
  list(p.value = p.value)
}

@@

# Set variables
n <- 100
ar <- 0.5
counter <- 0
nrep <- 1000
B <- 1000
mean <- 0
sd <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), 
                                              "pnorm", 
                                              B = B, 
                                              mean = mean, 
                                              sd = sd))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), 
                                                mean = mean, 
                                                sd = sd)$p.value)

@@

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(ma = 0.5), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n), 
                                              "pnorm", 
                                              B = B,
                                              mean = mean,
                                              sd = sd))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ma = 0.5), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n),
                                                mean = mean,
                                                sd = sd)$p.value)

@@

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(ar = ar, 
                                                           ma = ma), 
                                                      rand.gen=rnorm, 
                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
                                                      n = n), 
                                            "pnorm", 
                                            B = B,
                                            mean = mean,
                                            sd = sd))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ar = ar, 
                                                           ma = ma), 
                                                      rand.gen=rnorm, 
                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
                                                      n = n),
                                                mean = mean,
                                                sd = sd)$p.value)

@@

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(order = c(2, 0, 0), 
                                                           ar = c(b1, b2)),
                                                      rand.gen=rnorm,
                                                      sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)),
                                                      n = n), 
                                            "pnorm", 
                                            B = B,
                                            mean = mean,
                                            sd = sd))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(order = c(2, 0, 0), 
                                                           ar = c(b1, b2)),
                                                      rand.gen=rnorm,
                                                      sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)),
                                                      n = n),
                                                mean = mean,
                                                sd = sd)$p.value)

@@

```{r Gamma D}
# Testing bootstrap with copulas for gamma distribution
test_gamma_D <- function(x, dist, B = 100, wcopula = normalCopula, shape, scale) {

    # Get observed stat
    n <- length(x)

        # Calculate new test statistic
        stat.b[i] <- ks.test(x.b, dist, shape = shape, scale = scale)$statistic
    }

# Naive function that incorrectly uses fitted parameters for gamma distribution
test_standard_gamma <- function(x, shape, scale) {
  p.value <- ks.test(x, "pgamma", shape = shape, scale = scale)$p.value
  list(p.value = p.value)
}

@@

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_gamma_D(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
                                             "pgamma", 
                                             B = B,
                                             shape = shape,
                                             scale = scale))
counter <- 0

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_standard_gamma(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
                                                   shape = shape, 
                                                   scale = scale)$p.value)

@@

```{r GEV D}
# Testing bootstrap with copulas for GEV distribution
test_gev_D <- function(x, B = 100, wcopula = normalCopula, loc, scale, shape) {

    # Get observed stat
    stat  <- ks.test(x, 'pgev', loc = loc, scale = scale, shape = shape)$statistic

        # Transform the bootstrap sample
        x.b <- qgev(u, loc = loc, scale = scale, shape = shape)

        # Calculate bootstrap test statistic
        stat.b[i] <- ks.test(x.b, 'pgev', loc = loc, scale = scale, shape = shape)$statistic
    }

# Standard KS test for GEV distribution
test_standard_gev <- function(x, loc, scale, shape) {
  p.value <- ks.test(x, "pgev", loc = loc, scale = scale, shape = shape)$p.value
  list(p.value = p.value)
}

@@

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_gev_D(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho),
                                           loc = loc, 
                                           shape = shape,
                                           scale = scale,
                                           B = B))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_gev(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
                                                 loc = loc, 
                                                 shape = shape,
                                                 scale = scale)$p.value)

@@

    ## transform the data to standard normal scale and fit arma(1,1)
    zx <- qnorm(rank(x) / (n + 1))
    fit <- tseries::arma(zx, include.intercept = FALSE)

    ar <- fit$coef[1]
    ma <- fit$coef[2]

@@

test_standard_ks <- function(x, pdist, ...) {
  p.value <- ks.test(x, pdist, ...)$p.value
  list(p.value = p.value)
}

@@

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D2(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), 
                                              pnorm, 
                                              qnorm,
                                              mean = mean, 
                                              sd = sd,
                                              B = B))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), 
                                                pnorm,
                                                mean = mean, 
                                                sd = sd)$p.value)

@@

save(results, file = "results_ar1_D2.RData")

@@

```{r MA(1) D2}
# Set variables
n <- 100
ar <- 0.5
ma <- 0.5
counter <- 0
nrep <- 1000
B <- 1000
mean <- 0
sd <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D2(arima.sim(list(ma = ma), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n), 
                                              pnorm, 
                                              qnorm,
                                              mean = mean, 
                                              sd = sd,
                                              B = B))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ma = ma), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n), 
                                                pnorm,
                                                mean = mean, 
                                                sd = sd)$p.value)

@@

save(results, file = "results_ma1_D2.RData")

@@

```{r ARMA(1,1) D2}
# Set variables
n <- 100
ar <- 0.5
ma <- 0.5
counter <- 0
nrep <- 1000
B <- 1000
mean <- 0
sd <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D2(arima.sim(list(ar = ar, 
                                                           ma = ma), 
                                                      rand.gen=rnorm, 
                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
                                                      n = n), 
                                              pnorm, 
                                              qnorm,
                                              mean = mean, 
                                              sd = sd,
                                              B = B))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ar = ar, 
                                                           ma = ma), 
                                                      rand.gen=rnorm, 
                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
                                                      n = n), 
                                                pnorm,
                                                mean = mean, 
                                                sd = sd)$p.value)

@@

save(results, file = "results_arma_D2.RData")

@@

```{r AR(2) D2}
# Set variables
n <- 100
b1 <- 0.5
b2 <- 0.3
counter <- 0
nrep <- 1000
B <- 1000
mean <- 0
sd <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D2(arima.sim(list(order = c(2, 0, 0), 
                                                           ar = c(b1, b2)),
                                                      rand.gen=rnorm,
                                                      sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)),
                                                      n = n), 
                                              pnorm, 
                                              qnorm,
                                              mean = mean, 
                                              sd = sd,
                                              B = B))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(order = c(2, 0, 0), 
                                                           ar = c(b1, b2)),
                                                      rand.gen=rnorm,
                                                      sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)),
                                                      n = n), 
                                                pnorm,
                                                mean = mean, 
                                                sd = sd)$p.value)

@@

save(results, file = "results_ar2_D2.RData")

@@

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D2(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
                                             pgamma, 
                                             qgamma,
                                             shape = shape,
                                             scale = scale,
                                             B = B))
counter <- 0

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_standard_ks(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
                                                pgamma,
                                                shape = shape,
                                                scale = scale)$p.value)

@@

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D2(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho),
                                               pgev,
                                               qgev,
                                               loc = loc, 
                                               shape = shape,
                                               scale = scale,
                                               B = B))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
                                                 pgev,
                                                 loc = loc, 
                                                 shape = shape,
                                                 scale = scale)$p.value)

>>>>

```{r packages}
# Load packages
library(tidyverse)
library(copula)
library(evd)
library(ismev)
library(tseries)
library(forecast)
source('tspb.R')
```

@@

```{r AR(1) D}
test_copula_D <- function(x, pdist, qdist, ..., B, wcopula = normalCopula) {

@@

    stat  <- ks.test(x, pdist, ...)$statistic

@@

        # Transform bootstrap sample and fit the parameters
        x.b <- qdist(u, ...)

@@

# Standard KS test
test_standard_ks <- function(x, pdist, ...) {
  p.value <- ks.test(x, pdist, ...)$p.value
  list(p.value = p.value)
}

@@

# Set variables
n <- 100
ar <- 0.5
counter <- 0
nrep <- 1000
B <- 100
mean <- 0
sd <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D(genData(n = 100, qdist = qnorm, mean = 0, sd = 1, copula = claytonCopula, rho = 0.5), 
                                              pdist = pnorm, 
                                              qdist = qnorm,
                                              mean = mean,
                                              sd = sd,
                                              B = B, 
                                              wcopula = normalCopula))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(genData(n = 100, qdist = qnorm, mean = 0, sd = 1, copula = claytonCopula, rho = 0.5), 
                                                pdist = pnorm,
                                                mean = mean, 
                                                sd = sd)$p.value)

@@

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(ma = 0.5), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n), 
                                              pdist = pnorm, 
                                              qdist = qnorm,
                                              mean = mean,
                                              sd = sd,
                                              B = B,
                                              wcopula = normalCopula))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ma = 0.5), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n),
                                                pdist = pnorm,
                                                mean = mean,
                                                sd = sd)$p.value)

@@

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(ar = ar, 
                                                           ma = ma), 
                                                      rand.gen=rnorm, 
                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
                                                      n = n), 
                                            pdist = pnorm, 
                                            qdist = qnorm,
                                            mean = mean,
                                            sd = sd,
                                            B = B,
                                            wcopula = normalCopula))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ar = ar, 
                                                           ma = ma), 
                                                      rand.gen=rnorm, 
                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
                                                      n = n),
                                                pdist = pnorm,
                                                mean = mean,
                                                sd = sd)$p.value)

@@

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(order = c(2, 0, 0), 
                                                           ar = c(b1, b2)),
                                                      rand.gen=rnorm,
                                                      sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)),
                                                      n = n), 
                                            pdist = pnorm, 
                                            qdist = qnorm,
                                            mean = mean,
                                            sd = sd,
                                            B = B,
                                            wcopula = normalCopula))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(order = c(2, 0, 0), 
                                                           ar = c(b1, b2)),
                                                      rand.gen=rnorm,
                                                      sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)),
                                                      n = n),
                                                pdist = pnorm,
                                                mean = mean,
                                                sd = sd)$p.value)

@@

```{r Gamma D}
ptm <- proc.time()

@@

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
                                             pdist = pgamma,
                                             qdist = qgamma,
                                             shape = shape,
                                             scale = scale,
                                             B = B,
                                             wcopula = normalCopula))
counter <- 0

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_standard_ks(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
                                                   pdist = pgamma,
                                                   shape = shape, 
                                                   scale = scale)$p.value)

@@

```{r GEV D}
ptm <- proc.time()

@@

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho),
                                           pdist = pgev,
                                           qdist = qgev,
                                           loc = loc, 
                                           shape = shape,
                                           scale = scale,
                                           B = B,
                                           wcopula = normalCopula))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
                                                 pdist = pgev,
                                                 loc = loc, 
                                                 shape = shape,
                                                 scale = scale)$p.value)

@@

    ## transform the data to standard normal scale and fit arma(1,1)
    zx <- qnorm(rank(x) / (n + 1))

    fit <- tseries::arma(zx, include.intercept = FALSE)
    ar <- fit$coef[1]
    ma <- fit$coef[2]

@@

@@

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D2(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), 
                                              pdist = pnorm, 
                                              qdist = qnorm,
                                              mean = mean, 
                                              sd = sd,
                                              B = B))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), 
                                                pdist = pnorm,
                                                mean = mean, 
                                                sd = sd)$p.value)

@@

#save(results, file = "results_ar1_D2.RData")

@@

```{r MA(1) D2}
# Set variables
n <- 100
ar <- 0.5
ma <- 0.5
counter <- 0
nrep <- 1000
B <- 100
mean <- 0
sd <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D2(arima.sim(list(ma = ma), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n), 
                                              pdist = pnorm, 
                                              qdist = qnorm,
                                              mean = mean, 
                                              sd = sd,
                                              B = B))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ma = ma), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n), 
                                                pdist = pnorm,
                                                mean = mean, 
                                                sd = sd)$p.value)

@@

#save(results, file = "results_ma1_D2.RData")

@@

```{r ARMA(1,1) D2}
# Set variables
n <- 100
ar <- 0.5
ma <- 0.5
counter <- 0
nrep <- 1000
B <- 100
mean <- 0
sd <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D2(arima.sim(list(ar = ar, 
                                                           ma = ma), 
                                                      rand.gen=rnorm, 
                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
                                                      n = n), 
                                              pdist = pnorm, 
                                              qdist = qnorm,
                                              mean = mean, 
                                              sd = sd,
                                              B = B))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ar = ar, 
                                                           ma = ma), 
                                                      rand.gen=rnorm, 
                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
                                                      n = n), 
                                                pdist = pnorm,
                                                mean = mean, 
                                                sd = sd)$p.value)

@@

#save(results, file = "results_arma_D2.RData")

@@

```{r AR(2) D2}
# Set variables
n <- 100
b1 <- 0.5
b2 <- 0.3
counter <- 0
nrep <- 1000
B <- 100
mean <- 0
sd <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D2(arima.sim(list(order = c(2, 0, 0), 
                                                           ar = c(b1, b2)),
                                                      rand.gen=rnorm,
                                                      sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)),
                                                      n = n), 
                                              pdist = pnorm, 
                                              qdist = qnorm,
                                              mean = mean, 
                                              sd = sd,
                                              B = B))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(order = c(2, 0, 0), 
                                                           ar = c(b1, b2)),
                                                      rand.gen=rnorm,
                                                      sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)),
                                                      n = n), 
                                                pdist = pnorm,
                                                mean = mean, 
                                                sd = sd)$p.value)

@@

#save(results, file = "results_ar2_D2.RData")

@@

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D2(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
                                             pdist = pgamma, 
                                             qdist = qgamma,
                                             shape = shape,
                                             scale = scale,
                                             B = B))
counter <- 0

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_standard_ks(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
                                                pdist = pgamma,
                                                shape = shape,
                                                scale = scale)$p.value)

@@

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D2(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho),
                                               pdist = pgev,
                                               qdist = qgev,
                                               loc = loc, 
                                               shape = shape,
                                               scale = scale,
                                               B = B))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
                                                 pdist = pgev,
                                                 loc = loc, 
                                                 shape = shape,
                                                 scale = scale)$p.value)
